Evolutionary Learning of Policies for MCTS Simulations

### 2012-03-18 thesis/paper/paper.tex
Removed old commented sections from thesis conversion.
6 TODO's left out of 13 total comments... about halfway there.

\title{Evolutionary Learning of Policies for MCTS Simulations}
\numberofauthors{2}
\author{ 
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
James Pettit \\
       \affaddr{U.C. Santa Cruz}\\
       \affaddr{Santa Cruz, California}\\
       \email{ jpettit@soe.ucsc.edu}
% 2nd. author
\alignauthor
David Helmbold \\
       \affaddr{U.C. Santa Cruz}\\
       \affaddr{Santa Cruz, California}\\
       \email{dph@soe.ucsc.edu}
}

@@

\section{Introduction}
Abstract strategy games provide an attractive testbed for artificial intelligence and machine learning applications. The game framework provides immediate feedback on algorithm performance. 
%The choice of game and rules can also be experimentally varied to give a range of difficulty and computational complexity levels. 
Starting with mathematical game theory research, the most common technique for game AI has been brute force search of the tree of legal moves. 
This technique, highly tuned and optimized, is what led to Chinook's ascendance to World Champion in 1994 and Deep Blue's eventual victory in 1997 over then World Champion Gary Kasparov. These victories cemented brute force tree search as standard techniques in abstract strategy games, to the point where computers constructing endgame tables have been strong enough to find sequences lasting for hundreds of moves. Kasparov himself suggested a version of Chess that allowed the player to consult a computer for move advice. Chinook went so far as to solve checkers, proving that perfect play will end in a draw. 
Several games, such as  Checkers, Chess, and Othello, have good enough evaluation functions and few enough legal moves so that that brute force tree search techniques can beat the best human players.

@@

%Go is a much older game than Hex, and much research has been done on Go playing algorithms. 
Despite its simpler rules, Hex has a similar branching factor as Go and long-range interactions make it difficult to 
evaluate Hex positions.
Although we emphasize Hex here, the techniques we propose generalize to any cutting and connecting game
(such as Go or Havannah).

@@

\begin{figure}
	\begin{center}
%	\centerline{\begin{HexBoard}[board size=5]
%		\HGame{a3,c2}
%	\end{HexBoard}
%	}
	\includegraphics[width=3.0in]{graphics/tree.pdf}
	\end{center}
	\caption{Partial MC Search Tree}
	\label{fig:tree}
\end{figure}

%As stated, the current top computer Hex player, MoHex, uses the open-source Fuego implementation of Monte-Carlo Tree Search (MCTS)~\cite{mohex}.

@@

All nodes in the tree correspond to a fixed board position, i.e.~the occupancy state of the board and which player is next to move. 
Nodes also have statistics associated with their position:  the number of winning simulations performed that used the node, and the total number of simulations that included the node. 
For each simulation the algorithm will start at the root node, recursively traverse the (partial) tree until it reaches a leaf node.
The simulation continues from the position represented by this leaf node until a winner is determined.
The result of the simulation is used to update the statistics at nodes in the tree
(see Listing 1).
If the leaf node has been visited enough times (50 in our case), then it is expanded and nodes for all possible moves from 
that position are added to the search tree.

@@

Figure \ref{fig:tree} shows a partial Monte-Carlo search tree for the given position. In the example, the child-selection policy visited the node for \texttt{Black E4}, then \texttt{White A1}. 
The continuation policy ran, completing the game from the positiion with \texttt{E4} occupied by \hblack\ and \texttt{A1} occupied by \hwhite.
This resulted in a loss for \hblack. 
The update policy choose to update all nodes along the visited path, incrementing the wins for \hwhite\ moves and incrementing the losses for \hblack\ moves.

@@

The \verb+continue_from+ function plays out the rest of the game from the current position. 
The simplest policy, which we call the \emph{default policy},
 plays uniformly at random from the legal moves until the game ends (in Hex, when one player has a winning path). 
The continuation policy has a large effect on the strength of the MCTS player.
In fact, one of the top Go engines, MoGo, uses a near-zero exploration coefficient in its child selection policy,
putting most of the control of the search in the hands of the continuation policy~\cite{gelly2007combining}.
% and the Go literature has a large body of work dedicated to improving it.
Initial research in MCTS Go players focused on using a strong continuation policy, with expert-derived heuristics to select the next move~\cite{chaslot2010adding}. 
The top Computer Go programs all have complex hand-crafted policies with rules to examine the current position and select a ``good'' move to play, possibly with a stochastic choice between several candidates. 
Only when none of the rules match do they fall back to a uniform random move. 
It was quickly found that building a stronger continuation policy does not guarantee better performance when used in the full tree search~\cite{gelly2006modification}. 
In other words, when the continuation policies are used as players, the relative strengths of the continuation policies are poor predictors
of how well the MCTS algorithms relying on these continuation policies will perform.
This surprising result may be due to stronger continuation policies under-exploring the search space.
In any case, this means that hand crafting an effective continuation policy requires benchmarking and frequent tests of the entire
MCTS system as small changes to the simulation policy can have unpredictable effects on overall performance.
This illustrates the need for automated systems for tuning the continuation policy.

@@

\subsection{Update Policy}
Once a simulation is finished, the result is used to update the search tree.
Basic MCTS systems updated the win and visit statistics only along the traversed path.
It was quickly discovered that more aggressive update strategies are often profitable.
One simple example is the All-Moves-As-First (AMAF) heuristic~\cite{brugmann1993monte}
that exploits the fact that moves played in a simulation could have been played in any order. 
Thus, a move deep in the simulation could be fictitiously treated as the ``first'' move from an intermediate position. 
In addition to updating the statistics of the nodes in the path, all children of nodes on the path corresponding to moves made later
in the simulation also have their AMAF win and visit counts updated. 
%Variations on AMAF have been tested, including Permutations AMAF, which updates a node if any permutation of the simulation contained the node's position, and Some-Moves-As-First, which attempts to restrict the number of siblings updated.

@@

% TODO
%\textbf{does MoHex do something fancier?}
% MoHex uses one local pattern - bridge preservation, and AMAF updates with RAVE (http://webdocs.cs.ualberta.ca/~hayward/hex/#mohex)

@@

Hivemind is a system that learns to play abstract strategy games on a regular board. 
The system consists of three modules: the evolutionary learning process, a Monte-Carlo based UCT search tree implementation, and a ``Game Tracker interface'' used by the tree search to maintain game state information. 
The design was influenced by Fuego, although Hivemind is written in a different language (Google's Go~\cite{golang}). 
In particular, the tracker interface is very similar to Fuego's subclassing system for implementing multiple games~\cite{Fuego}. 
Hivemind's tracker interface is currently implemented for the games of Hex, Go, and Tic-Tac-Toe. 
The major contribution of Hivemind is the integration of evolutionary learning to automatically learn appropriate continuation policies.
% Hivemind is also open-source software, available at \url{http://github.com/etherealmachine/hivemind}.
Preliminary work tried learning with particle swarm optimization, but we found that evolution strategies gave
superior results.

@@

Each empty location around this last move is a candidate local response, and a pattern database gives each of these candidates a
weight indicating its relative importance.
During a continuation play-out, a candidate local response is selected with probability proportional to its weight.
Figures \ref{fig:localpattern} and \ref{fig:encoding} show graphically how a local patterns can be mapped to an integer. 
The orange marker denotes the last move played. 
In Hex there are less than $2 * 4^6=2^{13}$ possible local patterns, and 
assigning a weight to each of these patterns creates a continuation strategy.
Thus the continuation strategies we consider correspond to an array of $2^{13}$ weights, one for each local pattern.
% TODO
%\textbf{How about tenuki weights? does hivemind consider them?}
% Early experiments with tenuki weights were less successful. The default policy is only used if no legal moves exist in the local area.

@@

@@

The Game Tracker interface provides a simple definition of what is needed for a game to use the MCTS+UCT framework. 
%It also constrains the space of games that can be easily implemented in Hivemind. 
In particular, Hivemind is well suited for 2 player placement games with perfect information. 
Since node expansion uses the \texttt{Legal(color, vertex)} function to find all legal children,
Hivemind is not constrained to games with regular boards.

@@

Our implementation of EW works as follows.
\begin{enumerate}
\item An initial population (we use 30 individuals) is randomly generated. 
Each individual is represented by its vector of $2^{13}$ local pattern weights 
(each pattern weight is randomly chosen from $[0 .. 100]$)
and a strategy parameter $\sigma$ that controls how fast it evolves.
During assessment, the individual will also be assigned a real-valued ``fitness'' attribute.
\item The algorithm iterates the following with each iteration forming one ``generation'':
	\begin{enumerate}
	\item From the 30 parents, generate 35 children.
		\begin{enumerate}
		\item Each child is created by randomly selecting 2 parents and then 
		averaging the parents' local patten weight vectors and strategy parameters.
		\item	The child's strategy parameter $\sigma$ is \emph{mutated} to $\sigma e^{ {\cal N}(0,\tau^2)}$
			(see below).
		\item Each local pattern weight of the child is mutated by adding a random variable drawn from the Normal Distribution
		${\cal N}(0, \sigma^2)$.
		\end{enumerate}
	\item The best 5 performing parents are propagated through without mutation.  This is done to preserve well-performing solutions.
	\item Evaluate the fitness of the new pool of 40 individuals, and keep only the top 30 as parents for the next generation.
	\end{enumerate}
\end{enumerate}

@@

%\begin{figure}
%\begin{flalign*}
%	\tau_{t} = & \frac{1}{\sqrt{2D}} \left(1 - \frac{\textrm{generation}}{\textrm{max generations}}\right) \\
%	\sigma_{t} = & \sigma_{t-1} e^{N(0, \tau^2)} \\
%	p_{i, t} = & p_{i, t-1} N(0, \sigma_{t}^2)
%\end{flalign*}
%\caption{Differential equations for $\tau$, $\sigma$, and $\bf{p}$, indexed by time $t$. $D$ is the number of dimensions, i.e. $|\bf{p}|$}
%\label{mutate}
%\end{figure}
%

\subsubsection*{Fitness Evaluation}
%\label{fitness}

Every generation, each individual plays $n=5$ complete games against opponents chosen  randomly from the pool.
Opponents are drawn with replacement, so a given individual could play the same opponent more than once each generation. 
At the beginning of each game, one of the two players is randomly chosen to play \hblack, the other to play \hwhite. 
A swap-safe move was used to play the first move to greatly reduce the first-mover advantage. 
The winner of each game receives 1 point added to their fitness, the loser has 1 point deducted from their fitness.
This means that individuals will be evaluated on about $10$ games, but the exact number depends on how often they are
chosen as opponents.

%\subsection{The Hivemind System}
%Hivemind was designed for experiments in learning to play abstract strategy games on a regular board. The system consists of three modules: the evolutionary learning process, a Monte-Carlo based UCT search tree implementation, and a ``Game Tracker interface'' used by the tree search to maintain game state information. The design was influenced by Fuego, although Hivemind is written in a different language (Google's Go~\cite{golang}). In particular, the tracker interface is very similar to Fuego's subclassing system for implementing multiple games~\cite{Fuego}. Hivemind's tracker interface is currently implemented for the games of Hex, Go, and Tic-Tac-Toe. The major contribution of Hivemind is the integration of evolutionary learning into the search process. Hivemind is also open-source software, available at \url{http://github.com/etherealmachine/hivemind}.
%
%\subsubsection{Learning}\label{learning}
%The learning module is responsible for driving the evolutionary search process. In general, the learning module is responsible for finding a strategy (described in Section \ref{esmods}) that performs well during the evaluation step. Hivemind currently uses Evolution Strategies, although previous versions experimented with Particle Swarm Optimization. Selection and mutation are implemented as described in section \ref{estrats}. Evaluation is described in section~\ref{fitness}. 
%
%\subsubsection{Search}
%The search module is a simple generic implementation of Monte-Carlo Tree Search, using the UCT algorithm to traverse the tree. Section \ref{mcts} has a description of the MCTS process. The search module uses the Game Tracker to expand the tree and perform the random playouts. The entire source code for search is only about 600 lines of code. Using some extra information from the Game Tracker, search is configurable to use RAVE and AMAF heuristics to update multiple nodes using the results of a single playout.
%
%\subsubsection{Game Tracker}
%The Game Tracker allows complete games to be played vi Monte-Carlo Tree Search. The implementation of a game has four responsibilities:
%\begin{enumerate}
%\item{Maintain all required game state. A single function, \texttt{Play(color, vertex)}, is used by the search tree to apply a move for the given color.}
%\item{Report legal moves from a given game state. The \texttt{Legal(color, vertex)} function is used to query the legality of a given move. The search tree uses this to expand a parent node, adding all legal moves as children.}
%\item{Report on the status of the winner. The \texttt{Winner()} function is used to determine the current winner of the game. The special \texttt{Empty} player is returned while the game is in progress, and either \hblack{} or \hwhite{} once a winner has been determined.}
%\item{Playing out the game from the current game state. The tracker is parameterized with the policy weights, and responsible for using them during the playout. The speed of the playout function is also critical, as more playouts-per-second generally result in better move selection. This emphasis on speed is why the tracker is required to implement a monolithic \texttt{Playout} function. Many games have optimizations that can be performed in the playout that the search tree is unaware of, for example, the Hex tracker keeps a simple list of randomized empty positions, so random move selection is a O(1) operation. This is because in Hex, any empty position is legal. This is not the case for Go, so the Go engine uses other optimizations for fast random move selection.}
%\end{enumerate}
%The additional \texttt{WasPlayed(color, vertex)} function provides information required for the AMAF heuristic. A few extra functions also provide for debugging by pretty-printing the tracker's internal state.
%
%The Game Tracker interface provides a simple definition of what is needed for a game to use the MCTS+UCT framework. It also constrains the space of games that can be easily implemented in Hivemind. In particular, Hivemind allows for 2 player games with perfect information. The game space is not required to be a regular board. Node expansion uses the \texttt{Legal(color, vertex)} function to find all legal children. Vertices are assumed to be numbered consecutively, so a tracker for a non-regular board can encode vertices as it wishes.

@@

%
%The fact that evolutionary learning can find weights that boost performance versus uniform local in the same manner that uniform 
% local improves upon pure random shows how much further there is to go, and shows the weaknesses of purely random simulations.

@@

%\begin{figure}[t]
%	\begin{center}
%		\begin{tabular}{c c}
%		& Default \\
%		\hline
%		Learned 1 & 91.0\% \\
%		Learned 2 & 90.5\% \\
%		Learned 3 & 90.5\% \\
%		Learned 4 & 87.5\% \\
%		Learned 5 & 90.5\% \\
%		Learned 6 & 93.5\% \\
%		Learned 7 & 93.0\% \\
%		Learned 8 & 91.5\% \\
%		Learned 9 & 87.0\% \\
%		Learned 10 & 92.5\% \\
%		Min & 87.0\% \\
%		Max & 93.5\% \\
%		Mean & 90.75\% \\
%		Std. Dev. & ~2.14\% \\
%		\end{tabular}
%		\caption{Results of 10 independent evolutionary processes versus the default policy. Percentage shown is average win-rate of row player versus column player.}
%		\label{fig:a1results}
%	\end{center}
%\end{figure}

@@

%\begin{figure}[t]
%	\begin{center}
%		\begin{tabular}{c c c c}
%		& Learned \\
%		Default 11x11 & 96.8\% \\
%		Default 13x13 & 100.0\% \\
%		Uniform 11x11 & 82.76\% \\
%		Uniform 13x13 & 92.86\% \\
%		\hline
%		\end{tabular}
%		\caption{Results of evolutionary process learned on a 7x7 board, playing on an 11x11 and 13x13 board. Percentage shown is average win-rate of column player versus row player.}
%		\label{fig:a2results}
%	\end{center}
%\end{figure}

The time required to learn greatly depends on the boardsize used. For training, a boardsize of 7x7 was chosen as a tradeoff between computation time and bias toward first-mover advantage. 
We now examine how well the policy learned on 7x7 boards generalizes to larger boards. 
We played 200 game matches on 11x11 and 13x13 boards between the learned policy and the 
default and uniform local policies.  
Because of the increased boardsize,  each player used 100,000 simulated playouts per move.

@@

It is worth emphasizing 
that  the learned continuation policies are coupled with relatively naive update and child-selection
polices.  
There is still a large gap between the automatically learned Hivemind policy and current champion programs,
but it remains to be seen how much of this gap can be closed with improved child-selection and update policies.

@@

%\newpage

>>>>

\title{Evolutionary Learning of Policies for MCTS Simulations}
\numberofauthors{2}
\author{ 
% 1st. author
\alignauthor
James Pettit \\
       \affaddr{U.C. Santa Cruz}\\
       \affaddr{Santa Cruz, California}\\
       \email{ jpettit@soe.ucsc.edu}
% 2nd. author
\alignauthor
David Helmbold \\
       \affaddr{U.C. Santa Cruz}\\
       \affaddr{Santa Cruz, California}\\
       \email{dph@soe.ucsc.edu}
}

@@

\section{Introduction}
Abstract strategy games provide an attractive testbed for artificial intelligence and machine learning applications. The game framework provides immediate feedback on algorithm performance. 
Starting with mathematical game theory research, the most common technique for game AI has been brute force search of the tree of legal moves. 
This technique, highly tuned and optimized, is what led to Chinook's ascendance to World Champion in 1994 and Deep Blue's eventual victory in 1997 over then World Champion Gary Kasparov. These victories cemented brute force tree search as standard techniques in abstract strategy games, to the point where computers constructing endgame tables have been strong enough to find sequences lasting for hundreds of moves. Kasparov himself suggested a version of Chess that allowed the player to consult a computer for move advice. Chinook went so far as to solve checkers, proving that perfect play will end in a draw. 
Several games, such as  Checkers, Chess, and Othello, have good enough evaluation functions and few enough legal moves so that that brute force tree search techniques can beat the best human players.

@@

Despite its simpler rules, Hex has a similar branching factor as Go and long-range interactions make it difficult to 
evaluate Hex positions.
Although we emphasize Hex here, the techniques we propose generalize to any cutting and connecting game
(such as Go or Havannah).

@@

\begin{figure}
	\begin{center}
	\includegraphics[width=3.0in]{graphics/tree.pdf}
	\end{center}
	\caption{Partial MC Search Tree}
	\label{fig:tree}
\end{figure}

@@

All nodes in the tree correspond to a fixed board position, i.e.~the occupancy state of the board and which player is next to move. 
Nodes also have statistics associated with their position:  the number of winning simulations performed that used the node, and the total number of simulations that included the node. 
For each simulation the algorithm will start at the root node, recursively traverse the (partial) tree until it reaches a leaf node.
The simulation continues from the position represented by this leaf node until a winner is determined.
The result of the simulation is used to update the statistics at nodes in the tree
(see Listing 1).
If the leaf node has been visited enough times (50 in our case), then it is expanded and nodes for all possible moves from 
that position are added to the search tree.
% TODO 7
% comment: how did you come with the constant of 50?
% answer: balancing exploration versus computational requirements and preliminary results
% also, this was suggested as a good starting point in the computer Go mailing list (5, 10, and 50 were some common values)

@@

Figure \ref{fig:tree} shows a partial Monte-Carlo search tree for the given position. In the example, the child-selection policy visited the node for \texttt{Black E4}, then \texttt{White A1}. 
The continuation policy ran, completing the game from the positiion with \texttt{E4} occupied by \hblack\ and \texttt{A1} occupied by \hwhite.
This resulted in a loss for \hblack. 
The update policy updates all nodes along the visited path, incrementing the wins for \hwhite\ moves and incrementing the losses for \hblack\ moves.

@@

The \verb+continue_from+ function plays out the rest of the game from the current position. 
The simplest policy, which we call the \emph{default policy},
 plays uniformly at random from the legal moves until the game ends (in Hex, when one player has a winning path). 
The continuation policy has a large effect on the strength of the MCTS player.
In fact, one of the top Go engines, MoGo, uses a near-zero exploration coefficient in its child selection policy,
putting most of the control of the search in the hands of the continuation policy~\cite{gelly2007combining}.
Initial research in MCTS Go players focused on using a strong continuation policy, with expert-derived heuristics to select the next move~\cite{chaslot2010adding}. 
The top Computer Go programs all have complex hand-crafted policies with rules to examine the current position and select a ``good'' move to play, possibly with a stochastic choice between several candidates. 
Only when none of the rules match do they fall back to a uniform random move. 
It was quickly found that building a stronger continuation policy does not guarantee better performance when used in the full tree search~\cite{gelly2006modification}. 
In other words, when the continuation policies are used as players, the relative strengths of the continuation policies are poor predictors
of how well the MCTS algorithms relying on these continuation policies will perform.
This surprising result may be due to stronger continuation policies under-exploring the search space.
In any case, this means that hand crafting an effective continuation policy requires benchmarking and frequent tests of the entire
MCTS system as small changes to the simulation policy can have unpredictable effects on overall performance.
This illustrates the need for automated systems for tuning the continuation policy.

@@

\subsection{Update Policy}
Once a simulation is finished, the result is used to update the search tree.
Basic MCTS systems updated the win and visit statistics only along the traversed path.
It was quickly discovered that more aggressive update strategies are often profitable.
One simple example is the All-Moves-As-First (AMAF) heuristic~\cite{brugmann1993monte}
that exploits the fact that moves played in a simulation could have been played in any order. 
Thus, a move deep in the simulation could be fictitiously treated as the ``first'' move from an intermediate position. 
In addition to updating the statistics of the nodes in the path, all children of nodes on the path corresponding to moves made later
in the simulation also have their AMAF win and visit counts updated.

@@

@@

Hivemind is a system that learns to play abstract strategy games on a regular board. 
The system consists of three modules: the evolutionary learning process, a Monte-Carlo based UCT search tree implementation, and a ``Game Tracker interface'' used by the tree search to maintain game state information. 
The design was influenced by Fuego, although Hivemind is written in a different language (Google's Go~\cite{golang}). 
In particular, the tracker interface is very similar to Fuego's subclassing system for implementing multiple games~\cite{Fuego}. 
Hivemind's tracker interface is currently implemented for the games of Hex, Go, and Tic-Tac-Toe. 
The major contribution of Hivemind is the integration of evolutionary learning to automatically learn appropriate continuation policies.
Preliminary work tried learning with particle swarm optimization, but we found that evolution strategies gave
superior results.

@@

Each empty location around this last move is a candidate local response, and a pattern database gives each of these candidates a
weight indicating its relative importance.
During a continuation play-out, a candidate local response is selected with probability proportional to its weight.
Figures \ref{fig:localpattern} and \ref{fig:encoding} show graphically how a local patterns can be mapped to an integer. 
The orange marker denotes the last move played. 
In Hex there are less than $2 * 4^6=2^{13}$ possible local patterns, and 
assigning a weight to each of these patterns creates a continuation strategy.
Thus the continuation strategies we consider correspond to an array of $2^{13}$ weights, one for each local pattern.

@@

% TODO 9
% comment: would it be possible to include patterns/weights from competition-level programs such as MoGo (in Go)?
% answer: yes

@@

The Game Tracker interface provides a simple definition of what is needed for a game to use the MCTS+UCT framework. 
In particular, Hivemind is well suited for 2 player placement games with perfect information. 
Since node expansion uses the \texttt{Legal(color, vertex)} function to find all legal children,
Hivemind is not constrained to games with regular boards.

@@

Our implementation of ES works as follows.
\begin{enumerate}
\item An initial population (we use 30 individuals) is randomly generated. 
Each individual is represented by its vector of $2^{13}$ local pattern weights 
(each pattern weight is randomly chosen from $[0 .. 100]$)
and a strategy parameter $\sigma$ that controls how fast it evolves.
During assessment, the individual will also be assigned a real-valued ``fitness'' attribute.
\item The algorithm iterates the following with each iteration forming one ``generation'':
	\begin{enumerate}
	\item From the 30 parents, generate 35 children.
		\begin{enumerate}
		\item Each child is created by randomly selecting 2 parents and then 
		averaging the parents' local patten weight vectors and strategy parameters.
		\item	The child's strategy parameter $\sigma$ is \emph{mutated} to $\sigma e^{ {\cal N}(0,\tau^2)}$
			(see below).
		\item Each local pattern weight of the child is mutated by adding a random variable drawn from the Normal Distribution
		${\cal N}(0, \sigma^2)$.
		\end{enumerate}
	\item The best 5 performing parents are propagated through without mutation.  This is done to preserve well-performing solutions.
	% TODO 10
	% comment: this appears to be against the spirit of natural evolution where mutation is always (presumably) present
	% answer: 5/35 children will be unmutated, so mutation is definitely still present in the system.
	% This is also standard in a lot the genetic algorithm literature.
	\item Evaluate the fitness of the new pool of 40 individuals, and keep only the top 30 as parents for the next generation.
	\end{enumerate}
\end{enumerate}

@@

\subsubsection*{Fitness Evaluation}

Every generation, each individual plays $n=5$ complete games against opponents chosen  randomly from the pool.
Opponents are drawn with replacement, so a given individual could play the same opponent more than once each generation. 
At the beginning of each game, one of the two players is randomly chosen to play \hblack, the other to play \hwhite. 
A swap-safe move was used to play the first move to greatly reduce the first-mover advantage. 
The winner of each game receives 1 point added to their fitness, the loser has 1 point deducted from their fitness.
This means that individuals will be evaluated on about $10$ games, but the exact number depends on how often they are
chosen as opponents.
% TODO 12
% comment: so the pool consisted of three basic policies? Why wasn't MoHex a part of the pool? In fact, the authors touch on this later in the paper:
% "A potential problem with self-learning is that the system might only be learning how to exploit the weaknesses of its competitors, and not making
% a general improvement in playing strength." This sentence is also problematic. Namely, it is unclear what a "general improvement in playing strength" is. A strong player against player A may be weak against player B. It is unclear how to define an opponent-independent measure of playing
% strength. However, by not including MoHex in the pool during the evolution the authors did not specifically evolve their continuation policies
% against MoHex. I wonder why.
% answer: To preserve MoHex as an outside comparator. Learning from self-play is also the research question.

@@

@@

@@

The time required to learn greatly depends on the boardsize used. For training, a boardsize of 7x7 was chosen as a tradeoff between computation time and bias toward first-mover advantage.
% TODO 13
% comment: explain
% answer: 
We now examine how well the policy learned on 7x7 boards generalizes to larger boards. 
We played 200 game matches on 11x11 and 13x13 boards between the learned policy and the 
default and uniform local policies.  
Because of the increased boardsize,  each player used 100,000 simulated playouts per move.

@@

It is worth emphasizing 
that  the learned continuation policies are coupled with relatively naive update and child-selection
polices.  
There is still a large gap between the automatically learned Hivemind policy and current champion programs,
but it remains to be seen how much of this gap can be closed with improved child-selection and update policies.
% TODO 13
% comment: yes, I think the results of this paper would be even more interesting if either (i) only continuation policies were compared
% e.g. by disabling all other techniques in MoHex) or (ii) other advanced techniques (e.g., child-selection policy, the update policy, etc.)
% were added to Hivemind as well.
% answer: Comparing just continuation policies is a tricky issue. Hivemind specifically scores candidates on winning a full game using MCTS, it does
% not attempt to build a strong continuation policy. It is true that a strong continuation policy can lead to stronger overall play, but especially
% the simulation balancing paper shows that strong playouts are not always the best approach to a stronger overall player.
% As to (ii), improving Hivemind's other areas is definitely a good idea

@@
